03 Data Vizualization

### 2023-02-16 03_data_viz.Rmd
fixed "Tunrda" typo, removed cairo library

```{r, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)    # CRAN v1.3.1    
library(forcats)      # CRAN v0.5.1      
#library(isoreader)    # CRAN v1.3.0    
#library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
#library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
library(readxl)       # CRAN v1.3.1       
library(ggsci)        # CRAN v2.9        
library(ggborderline) # [github::wurli/ggborderline] v0.1.0 
library(ggrepel)      # CRAN v0.9.1      
library(latex2exp)    # CRAN v0.5.0    
library(ggdist)       # CRAN v3.0.0       
library(ggsignif)     # CRAN v0.6.2     
library(ggridges)     # CRAN v0.5.3     
library(cowplot)      # CRAN v1.1.1      
library(scales)       # CRAN v1.1.1
library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3
library(Cairo)
```

@@

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  pivot_longer(
    cols = c(gen_d_weighted, gen_d_mc_weighted),
    names_to = "Correction",
    values_to = "gen_d"
  ) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = gen_d,
             fill = Correction)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
  labs(x = "Soil Type",
       y = "Weighted Mean Generation Time (d)") +
  theme_classic() +
  theme(
    legend.position = "NA",
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
p_gen_time_mean

p_ud_mean <- turnover_weighted %>% 
  pivot_longer(
    cols = c(u_d_weighted, u_d_mc_weighted),
    names_to = "Correction",
    values_to = "u_d"
  ) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>%
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = u_d,
             fill = Correction)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
  labs(
    x = "Soil Type",
    y = TeX("Weighted Mean Growth Rate $(d^{-1})$")
    ) +
  theme_classic() +
  theme(
    legend.position = "NA",
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
p_ud_mean

>>>>

```{r, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)    # CRAN v1.3.1    
library(forcats)      # CRAN v0.5.1      
#library(isoreader)    # CRAN v1.3.0    
#library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
#library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
library(readxl)       # CRAN v1.3.1       
library(ggsci)        # CRAN v2.9        
library(ggborderline) # [github::wurli/ggborderline] v0.1.0 
library(ggrepel)      # CRAN v0.9.1      
library(latex2exp)    # CRAN v0.5.0    
library(ggdist)       # CRAN v3.0.0       
library(ggsignif)     # CRAN v0.6.2     
library(ggridges)     # CRAN v0.5.3     
library(cowplot)      # CRAN v1.1.1      
library(scales)       # CRAN v1.1.1
library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3

@@

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  pivot_longer(
    cols = c(gen_d_weighted, gen_d_mc_weighted),
    names_to = "Correction",
    values_to = "gen_d"
  ) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tundra" )) %>% 
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = gen_d,
             fill = Correction)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
  labs(x = "Soil Type",
       y = "Weighted Mean Generation Time (d)") +
  theme_classic() +
  theme(
    legend.position = "NA",
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
p_gen_time_mean

p_ud_mean <- turnover_weighted %>% 
  pivot_longer(
    cols = c(u_d_weighted, u_d_mc_weighted),
    names_to = "Correction",
    values_to = "u_d"
  ) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tundra" )) %>%
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = u_d,
             fill = Correction)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
  labs(
    x = "Soil Type",
    y = TeX("Weighted Mean Growth Rate $(d^{-1})$")
    ) +
  theme_classic() +
  theme(
    legend.position = "NA",
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
p_ud_mean
